Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-08-09 ms.tex
more pre-submission edits

Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust by removing the mean cosmic IR 
background (CIB), as well as any instrumental offset. Additionally, faint 
residuals of the Solar dipole remain at low frequencies. We will address these 
issues by separately solving two sub-problems: first, fixing the absolute zero 
level of \PLANCK~857 GHz relative to external data, and second fitting 
100-545 GHz offsets and low order corrections by correlating these 
\PLANCK~bands against \PLANCK~857 GHz.

@@

Because of these ambiguities in the relationship between 857 GHz and 
H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level 
by comparison to the FDS99 857 GHz prediction. This renders our \PLANCK~857 GHz
absolute zero level tied indirectly to H\,\textsc{i} through the FDS99 
100$\mu$m and 240$\mu$m zero levels.

@@

In the course of this study we use not only \PLANCK~857 GHz, but also all of
the remaining \PLANCK~HFI bands, as well as \verb|i100|. To derive the 
zero level offsets that must be applied to each of the five lowest-frequency 
\PLANCK~bands, we perform a regression versus the \PLANCK~857 GHz map corrected
for the best-fit absolute zero level offset from $\S$\ref{sec:zp_abs}. We 
assume no offset need be applied to \verb|i100|, which already has its zero 
level tied to H\,\textsc{i}.

@@

With $p$ denoting a single $N_{side}$=64 HEALPix pixel \citep{healpix} in the 
maps $\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission, CMB anisotropies, and
compact sources removed. In the context of Equation \ref{equ:dip}, $\nu_i \in$ 
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ is the residual Solar dipole amplitude,
and its best-fit value represents the scaling of the Solar dipole that makes 
the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. $b$ 
represents the constant offset that must be subtracted from the band $\nu_i$ 
map to make its zero level consistent with that of the 857 GHz map. For each 
band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by performing a linear 
least squares fit with uniform weights and iterative outlier rejection. Figure 
\ref{fig:dip} shows scatter plots of the band $\nu_i$ versus 857 GHz 
correlation before and after correcting for the best-fit offset and residual 
dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only are the 
tightened correlations striking in these scatter plots, but the residual dipole
subtractions appear very successful in the two-dimensional band $\nu_i$ maps 
themselves. Before performing thermal dust fits, we therefore subtract the 
best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit 
offsets and residual dipole amplitudes are listed in Table \ref{table:offs},
along with other important per-band parameters, such as the fractional 
multiplicative calibration uncertainty $c_{\nu}$.

@@

At sufficiently high frequencies, Galactic thermal dust emission can be 
adequately modeled as a single MBB with power-law emissivity 
\citep[e.g. SFD;][]{planckdust}. However, it has long been recognized, 
particularly in view of the FIRAS spectra, that the dust SED flattens toward 
the millimeter in a manner which is not consistent with a simple extrapolation 
of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
found an improved fit to the FIRAS data using an empirically motivated 
superposition of two $\beta$=2 MBBs, one representing a `hot' grain population 
($T$$\approx$16$-$21 K), the other a `cold' grain population 
($T$$\approx$4$-$7 K). FDS99 built a more physically motivated two-MBB model, 
in which different grain emission/absorption properties account for the 
differing temperatures of each population, and these temperatures are coupled 
by assuming thermal equilibrium with the same interstellar radiation field 
(ISRF).

@@

Where $B_{\nu}$ is the Planck function, $T_1$ is the `cold' dust temperature, 
$T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
emissivity power-law indices of the cold and hot dust components respectively. 
$q_1$ represents the ratio of FIR emission cross section to optical absorption 
cross section for species 1, and similarly $q_2$ for species 2. $f_1$ and 
$f_2$ dictate the relative contributions of the two MBB components to the
combined SED, and can be thought of as encoding the mass fraction of each 
species, although technically $f_1$ ($f_2$) is the optical absorption 
cross-section weighted mass fraction for species 1 (2). Following the 
convention of FDS99, we choose $\nu_0$=3000 GHz and take $f_2$=(1$-$$f_1$).

@@

%Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. 
The color correction of Equation \ref{equ:bpcorr} therefore allows us to 
predict $\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the 
central frequency $\nu_{i,c}$ and then multiplying by factors 
$b_{\nu_i}(T, \beta)$. In practice, we interpolated the color corrections off 
of a set of precomputed, one-dimensional lookup tables each listing 
$b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the need to interpolate 
in both $\beta$ and $T$ by computing only a small set of one dimensional 
correction factors for the particular set of $\beta$ values of interest (e.g. 
$\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table \ref{tab:global}). This color 
correction approach makes the MCMC sampling described in $\S$\ref{sec:mcmc} 
much more computationally efficient by circumventing the need to perform the 
integral in the numerator of Equation \ref{equ:bpcorr} on-the-fly for each 
proposed dust temperature. We have chosen to compute the color corrections on a
per-MBB basis because this approach is very versatile; all possible 
two-component (and single-MBB) models are linear combinations of MBBs, so we 
can apply all of our color correction machinery even when we allow parameters 
other than temperature (e.g. $f_1$) to vary and thereby modify the dust 
spectrum shape.

@@

Lastly, we calculate the optimal single-MBB fit to the \PLANCK+DIRBE 
correlation slope spectrum. The best-fit single MBB has $\beta$=1.59, 
$T$=19.63, and $\chi^2_{\nu}$=5.65, indicating a significantly worse fit to the
data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
correlation slope analysis has confirmed the main conclusion of FDS99 and 
others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
just one, but, for the first time, independent of FIRAS. Still, it is apparent 
that the improvement in $\chi^2_{\nu}$ for single-MBB versus double MBB models 
found here is substantially less dramatic ($\Delta\chi^2_{\nu}$=4.32) than that
found in FDS99 ($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the 
exquisite narrow-band frequency coverage of FIRAS, especially near the dust SED
peak, which makes FIRAS a better suited data set than \PLANCK~for a detailed 
analysis of the globally best-fit dust SED model. In $\S$\ref{sec:hier}, we
confirm the basic conclusions of this section via an approach in which we 
allow the dust temperature to vary spatially. The analysis of $\S$7.5 also
allows us to confirm the conclusions of this section while including a 
fully detailed uncertainty model; our assumption of 2\% per-band uncertainties
on the correlation slopes is largely a statement that we seek a model
accurate to 2\% from 100-3000 GHz, although the fact that our $\chi^2_{\nu}$ 
values are order unity shows that the assumed uncertainties are not grossly 
over or underestimated.

@@

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
spatially constant. We employ the best-fit \PLANCK+DIRBE global parameters of 
Table \ref{tab:global}, model 2. For each line of sight, only the dust spectrum
normalization and dust temperatures are allowed to vary. In order to predict 
the dust SED for a given pixel, we are thus left with two remaining degrees of 
freedom, and must choose an appropriate set of two parameters to sample and 
thereby constrain via MCMC. To determine the SED normalization in each pixel, 
we draw samples in $\tilde{I}_{545}$, the `IRAS convention' intensity in the 
\PLANCK~545 GHz bandpass, as defined in Equation \ref{eqn:inten}. With the four
aforementioned global parameters fixed, the dust spectrum shape is determined 
entirely by the two dust temperatures, which are coupled. To constrain the dust
temperatures, we sample in $T_2$, the hot dust temperature. For each sample in 
$T_2$, we compute the corresponding value of $T_1$, thereby determining the 
temperature and emissivity power law index for both MBB components and thus 
fully specifying the SED shape. In principle, we could sample in either $T_1$ 
or $T_2$, but have chosen to sample in $T_2$ because emission from this 
component dominates in the relatively high frequency bands which most strongly 
constrain the dust temperatures.

@@

\begin{equation} \label{equ:like}
\mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\mathbf{I}-\mathbf{\tilde{I}})\Sigma^{-1}(\mathbf{I}-\mathbf{\tilde{I}})^T\Big]
\end{equation}

@@

Here $\mathbf{\tilde{I}}$ is the vector of predicted observations 
based on Equation \ref{eqn:inten} and the proposed values of $\tilde{I}_{545}$ 
and $T_2$: $\mathbf{\tilde{I}} = $($\tilde{I}_{217}$, 
$\tilde{I}_{353}$, $\tilde{I}_{545}$, $\tilde{I}_{857}$, $\tilde{I}_{3000}$). 
$\Sigma$ is the covariance matrix constructed based on the uncertainties in the
observed intensities:

@@

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term represents an uncertainty due 
to our subtraction of the \verb|SMICA| CMB model. The analogous term in 
\cite{planckdust} Equation 7 is ($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. 
an uncertainty proportional to the CMB model amplitude in each pixel. Because 
this term's spatial dependence can imprint the CMB anisotropies on the derived 
parameters, we have chosen to replace \verb|SMICA|($p$) with a spatially 
constant, RMS value for the CMB amplitude, $\sigma_{CMB, \nu_i}$. 
$\delta O_{\nu_i}$ represents the uncertainty in the band $\nu_i$ zero level 
offset, and the values of $\delta O_{\nu_i}$ can be read off from the second 
column of Table \ref{table:offs}. $n_{\nu_i}$ represents the instrumental noise
in band $\nu_i$. Because using per-pixel noise estimates based on the \PLANCK~
\verb|ii_cov| parameter can imprint features of the survey pattern onto the 
derived parameters, we have adopted a conservative, spatially constant value of
$n_{\nu_i}$ for each band. These values of $n_{\nu_i}$ are listed in Table 
\ref{table:offs}. The next term accounts for the uncertainty on the CO emission
correction, taking $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$ (see 
$\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).

@@

Lastly, during post burn-in sampling, we also estimate the monochromatic 
two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and the 
545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
$M_{545}$ are more readily useful than the sampling parameters themselves for 
translating our fit results into predictions of reddening ($\S$\ref{sec:ebv}) 
and thermal dust emission ($\S$\ref{sec:lofreq}), respectively. At high
Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and
typical $\tilde{I}_{545}$ fractional uncertainty of 13\%. Figure \ref{fig:sed}
shows a summary of the observed SED and resulting best-fit two-component
model for a single $N_{side}$=2048 pixel, and Figure \ref{fig:post} 
shows posterior PDFs for three pixels. Figure \ref{fig:comparison} shows
a map of our derived hot dust temperature at full-resolution, for a patch
of sky in the Polaris flare region.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM full-sky map of $f_1$ derived from our
low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
with appreciable molecular emission, as defined in $\S$\ref{sec:mole}. Such 
pixels should not be trusted in this analysis, which is sensitive to the SED 
shape at low frequencies affected by CO line emission. Variations in $f_1$
along the ecliptic plane are spurious results of imperfect zodiacal light
subtractions. However, interesting astrophysical variations of $f_1$ 
are evident, particularly the trend of increasing $f_1$ with decreasing
Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
and the clouds with relatively high $f_1$ near the north Galactic pole.}
\end{center}
\end{figure}

@@

%%%\begin{figure}
%%%\begin{center}
%%%\epsfig{file=f1_lambert.eps, width=3.3in}
%%%\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
%%%allowed to vary, shown in Lambert projection to highlight the salient features 
%%%near the north Galactic pole.}
%%%\end{center}
%%%\end{figure}

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. A 
general trend of increasing $f_1$ towards lower Galactic latitudes is 
apparent. The other most salient features are the relatively low
values of $f_1$ in the Polaris flare, and the relatively high $f_1$ values
near the north Galactic pole.

@@

% add comment about high f_1 regions near NGP
% also add sentences referring reader to the two f_1 figures

@@

The posterior sampling framework thus far described also affords us an
opportunity to evaluate the goodness-of-fit for competing dust SED models, and 
thereby cross-check the conclusions of our correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue evaluating the 
posterior of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), 
including all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, 
and switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for each pixel, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$.

@@

We calculate $\chi^2_{\nu}$ for various dust SED models, independently 
minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
First, we consider single-MBB models with $\beta$ spatially constant (see the
black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, 
with $\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
$\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
$\beta$=1.59.

We also evaluated $\chi^2_{\nu}$ for single-MBB models in which
$\beta$ varies spatially. In these cases, we adopted the 0.5$^{\circ}$ 
resolution $\beta$ map from \cite{planckdust}. We started by calculating 
$\chi^2_{\nu}$ using the \cite{planckdust} temperature map, finding 
$\chi^2_{\nu}$=4.68. Note that in this case no per-pixel chi-squared 
minimization was involved, as we simply evaluated $\chi^2_{p}$ for each pixel 
based on the fully-specified \cite{planckdust} emission model. Next, we tested 
a single-MBB model for which we adopted the \cite{planckdust} $\beta$ map, but 
allowed the per-pixel temperature and normalization to vary so as to minimize 
$\chi^2_p$. In this case, we found $\chi^2_{\nu}$=2.51, effectively identical 
to the value found for the spatially constant $\beta$=1.57 single-MBB model. 
This is perhaps unsurprising, as the average $\beta$ value from 
\cite{planckdust} over the mask in question is $\langle\beta\rangle$=1.58. 
This result does suggest, however, that the half-degree variations in $\beta$ 
are not materially improving the goodness-of-fit over the full frequency range 
100-3000 GHz relative to a model with appropriately chosen spatially constant 
$\beta$.

@@

% but then we tried ECL cuts, and in combination with modest offsets, that 
% worked

@@

% mention that DR includes software to obtain emission and extinction 
% predictions

@@

%software utilities
%provide maps at multiple different nsides ?
%   -> if so, actually smooth the maps before rebinning, or leave 
%      undersampled?
% provide uncertainty maps for tau and T2 ??

@@

% in above paragraph, say which single-MBB beta(s) we find to be favored

>>>>

Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust by removing the mean cosmic IR 
background (CIB), as well as any instrumental offset. Additionally, faint 
residuals of the Solar dipole remain at low frequencies. We will address these 
issues by separately solving two sub-problems: first, we set the absolute zero 
level of \PLANCK~857 GHz relative to external data, and second we fit the 
100-545 GHz offsets and low order corrections by correlating these 
\PLANCK~bands against \PLANCK~857 GHz.

@@

Because of this ambiguity in the relationship between 857 GHz and H\,\textsc{i}
emission, we decided to instead constrain the \PLANCK~857 GHz zero level by 
comparison to the FDS99-predicted 857 GHz thermal dust emission. This renders 
our \PLANCK~857 GHz absolute zero level tied indirectly to H\,\textsc{i} 
through the FDS99 100$\mu$m and 240$\mu$m zero levels.

@@

In the course of this study we use not only \PLANCK~857 GHz, but also all of
the remaining \PLANCK~HFI bands, as well as \verb|i100|. To derive the 
zero level offsets that must be applied to each of the five lowest-frequency 
\PLANCK~bands, we perform a regression versus the \PLANCK~857 GHz map corrected
for the best-fit absolute zero level offset from $\S$\ref{sec:zp_abs}. We 
assume no offset need be applied to \verb|i100|, which already has its zero 
level tied to H\,\textsc{i} by SFD.

@@

With $p$ denoting a single $N_{side}$=64 HEALPix pixel \citep{healpix} in the 
maps $\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission, CMB anisotropies, and
compact sources removed. In the context of Equation \ref{equ:dip}, $\nu_i \in$ 
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ is the residual Solar dipole amplitude,
and its best-fit value represents the scaling of the Solar dipole that makes 
the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly linear. $b$ 
represents the constant offset that must be subtracted from the band $\nu_i$ 
map to make its zero level consistent with that of the 857 GHz map. For each 
band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by performing a linear 
least squares fit with uniform weights and iterative outlier rejection. Figure 
\ref{fig:dip} shows scatter plots of the band $\nu_i$ versus 857 GHz 
correlation before (left) and after (right) correcting for the best-fit offset 
and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
are the tightened correlations striking in these scatter plots, but the 
residual dipole subtractions appear very successful in the two-dimensional band
$\nu_i$ maps themselves. Before performing thermal dust fits, we therefore 
subtract the best-fit $b$ and $d\mathcal{D}$ from each 143-545 GHz map. The 
best-fit offsets and residual dipole amplitudes are listed in Table 
\ref{table:offs}, along with other important per-band parameters, such as the 
fractional multiplicative calibration uncertainty $c_{\nu}$.

@@

At sufficiently high frequencies, Galactic thermal dust emission can be 
adequately modeled as a single MBB with power-law emissivity 
\citep[e.g. SFD;][]{planckdust}. However, it has long been recognized, 
particularly in view of the FIRAS spectra, that the dust SED flattens toward 
the millimeter in a manner which is not consistent with a simple extrapolation 
of single-MBB models to low frequencies. In the diffuse ISM, \cite{reach95} 
found an improved fit to the FIRAS data using an empirically motivated 
superposition of two $\beta$=2 MBBs, one representing a `hot' grain population 
($T$$\approx$16$-$21 K), the other a `cold' grain population 
($T$$\approx$4$-$7 K). FDS99 built a more physically motivated two-MBB model, 
in which different grain emission/absorption properties account for the 
differing temperatures of each population, and these temperatures are coupled 
by assuming thermal equilibrium with the same interstellar radiation field 
(ISRF).

@@

Where $B_{\nu}$ is the Planck function, $T_1$ is the `cold' dust temperature, 
$T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
emissivity power-law indices of the cold and hot dust components respectively. 
$q_1$ represents the ratio of FIR emission cross section to optical absorption 
cross section for species 1, and similarly $q_2$ for species 2. $f_1$ and 
$f_2$ dictate the relative contributions of the two MBB components to the
combined SED. Thus, $f_1$ and $f_2$ can be thought of as encoding the mass 
fraction of each species, although technically $f_1$ ($f_2$) is the optical 
absorption cross-section weighted mass fraction for species 1 (2). Following 
the convention of FDS99, we choose $\nu_0$=3000 GHz and take $f_2$=(1$-$$f_1$).

@@

%Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. 
The color correction of Equation \ref{equ:bpcorr} therefore allows us to 
predict $\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the 
central frequency $\nu_{i,c}$ and then multiplying by factors 
$b_{\nu_i}(T, \beta)$. In practice, we interpolated the color corrections off 
of a set of precomputed, one-dimensional lookup tables each listing 
$b_{\nu_i}(T, \beta)$ for a single $\beta$ value as a function of $T$. We thus
avoided the need to interpolate in both $\beta$ and $T$ by computing only a 
small set of one dimensional correction factors for the particular set of 
$\beta$ values of interest (e.g. $\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table 
\ref{tab:global}). This color correction approach makes the MCMC sampling 
described in $\S$\ref{sec:mcmc} much more computationally efficient by 
circumventing the need to perform the integral in the numerator of Equation 
\ref{equ:bpcorr} on-the-fly for each proposed dust temperature. We have chosen 
to compute the color corrections on a per-MBB basis because this approach is 
very versatile; all possible two-component (and single-MBB) models are linear 
combinations of MBBs, so we can apply all of our color correction machinery 
even when we allow parameters other than temperature (e.g. $f_1$) to vary and 
thereby modify the dust spectrum shape.

@@

Lastly, we calculate the optimal single-MBB fit to the \PLANCK+DIRBE 
correlation slope spectrum. The best-fit single MBB has $\beta$=1.59, 
$T$=19.63, and $\chi^2_{\nu}$=5.65, indicating a significantly worse fit to the
data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
correlation slope analysis has confirmed the main conclusion of FDS99 and 
others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
just one, but, for the first time, independent of FIRAS. Still, it is apparent 
that the improvement in $\chi^2_{\nu}$ for single-MBB versus double MBB models 
found here is substantially less dramatic ($\Delta\chi^2_{\nu}$=4.32) than that
found in FDS99 ($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the 
exquisite narrow-band frequency coverage of FIRAS, especially near the dust SED
peak, which makes FIRAS a better suited data set than \PLANCK~for a detailed 
analysis of the globally best-fit dust SED model. In $\S$\ref{sec:hier}, we
confirm the basic conclusions of this section via an approach in which we 
allow the dust temperature to vary spatially. The analysis of $\S$7.5 also
allows us to confirm the conclusions of this section while including a 
fully detailed uncertainty model; our assumption of 2\% per-band uncertainties 
on the correlation slopes is largely a statement that we seek a model
accurate to 2\% from 100-3000 GHz, although the fact that our $\chi^2_{\nu}$ 
values are order unity suggests that the assumed uncertainties are not grossly 
over or underestimated.

@@

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
spatially constant. We employ the best-fit \PLANCK+DIRBE global parameters of 
Table \ref{tab:global}, model 2. For each line of sight, only the dust spectrum
normalization and dust temperatures are allowed to vary. In order to predict 
the dust SED for a given pixel, we are thus left with two remaining degrees of 
freedom, and must choose an appropriate set of two parameters to sample and 
thereby constrain via MCMC. To determine the SED normalization in each pixel, 
we draw samples in $\tilde{I}_{545}$, the `IRAS convention' intensity in the 
\PLANCK~545 GHz bandpass, as defined in Equation \ref{eqn:inten}. With the four
aforementioned global parameters fixed, the dust spectrum shape is determined 
entirely by the two dust temperatures, which are coupled. To constrain the dust
temperatures, we sample in $T_2$, the hot dust temperature. For each sample in 
$T_2$, we compute the corresponding value of $T_1$, thereby fully specifying 
the SED shape. In principle, we could sample in either $T_1$ or $T_2$, but have
chosen to sample in $T_2$ because emission from this component dominates in the
relatively high frequency bands which most strongly constrain the dust 
temperatures.

@@

\begin{equation} \label{equ:like}
\mathcal{L}(\mathbf{I}|\tilde{I}_{545}, T_2) = \textrm{exp}\Big[-\frac{1}{2}(\mathbf{I}-\mathbf{\tilde{I}})^T\Sigma^{-1}(\mathbf{I}-\mathbf{\tilde{I}})\Big]
\end{equation}

@@

Here $\mathbf{\tilde{I}}$ is the vector of predicted observations 
based on Equation \ref{eqn:inten} and the proposed values of $\tilde{I}_{545}$ 
and $T_2$: $\mathbf{\tilde{I}} = $($\tilde{I}_{217}$, 
$\tilde{I}_{353}$, $\tilde{I}_{545}$, $\tilde{I}_{857}$, $\tilde{I}_{3000}$). 
$\Sigma$ is the per-pixel covariance matrix constructed based on the 
uncertainties in the observed intensities:

@@

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term represents an uncertainty due 
to our subtraction of the \verb|SMICA| CMB model. The analogous term in 
\cite{planckdust} Equation 7 is ($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. 
an uncertainty proportional to the CMB model amplitude in each pixel. Because 
this term's spatial dependence can imprint the CMB anisotropies on the derived 
parameters, we have chosen to replace \verb|SMICA|($p$) with a spatially 
constant, RMS value for the CMB amplitude, $\sigma_{CMB, \nu_i}$. 
$\delta O_{\nu_i}$ represents the uncertainty in the band $\nu_i$ zero level 
offset, and the values of $\delta O_{\nu_i}$ can be read off from the second 
column of Table \ref{table:offs}. $n_{\nu_i}$ represents the instrumental noise
in band $\nu_i$. Because using per-pixel noise estimates based on the \PLANCK~
\verb|ii_cov| parameter can imprint features of the survey pattern onto the 
derived parameters, we have adopted a conservative, spatially constant value of
$n_{\nu_i}$ for each band. These values of $n_{\nu_i}$ are listed in Table 
\ref{table:offs}. The next term accounts for the uncertainty on the CO emission
correction, taking $\sigma_{CO, \nu_i}(p)$=0.15$\times$$I_{CO, \nu_i}(p)$ (see 
$\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).

@@

Lastly, during post burn-in sampling, we also estimate the monochromatic 
two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}, \beta_2) \rangle$, its variance, 
and the 545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
$M_{545}$ are more readily useful than the sampling parameters themselves for 
translating our fit results into predictions of reddening ($\S$\ref{sec:ebv}) 
and thermal dust emission ($\S$\ref{sec:lofreq}), respectively. At high 
Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and typical 
$\tilde{I}_{545}$ fractional uncertainty of 13\%. Figure \ref{fig:sed} shows a 
summary of the observed SED and resulting best-fit two-component model for a 
single $N_{side}$=2048 pixel, and Figure \ref{fig:post} shows posterior PDFs 
for three pixels. Figure \ref{fig:comparison} shows a map of our derived hot 
dust temperature at full-resolution, for a patch of sky in the Polaris flare 
region.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM full-sky map of $f_1$ derived from our
low-resolution fits described in $\S$\ref{sec:lores}. Red coloring masks pixels
with appreciable molecular emission, as defined in $\S$\ref{sec:mole}. Such 
pixels should not be trusted in this analysis, which is sensitive to the SED 
shape at low frequencies affected by CO line emission. Variations in $f_1$
along the ecliptic plane are spurious results of imperfect zodiacal light
subtractions. However, interesting astrophysical variations of $f_1$ 
are evident, particularly the trend of increasing $f_1$ with decreasing
Galactic latitude, the relatively low $f_1$ values in the Polaris flare region,
and the clouds with relatively high $f_1$ values the north Galactic pole.}
\end{center}
\end{figure}

@@

The resulting full-sky map of $f_1$ is shown in Figure \ref{fig:f1}. A 
general trend of increasing $f_1$ towards lower Galactic latitudes is 
apparent. The other most salient features are the relatively low
values of $f_1$ in the Polaris flare, and the relatively high $f_1$ clouds
near the north Galactic pole.

@@

@@

The posterior sampling framework thus far described also affords us an
opportunity to evaluate the goodness-of-fit for competing dust SED models, and 
thereby cross-check the conclusions of our correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue evaluating the 
posterior of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), 
including all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, 
and switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for pixel $p$, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$.

@@

We calculate $\chi^2_{\nu}$ for various dust SED models, independently 
minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
temperature and normalization, then evaluating 
$\langle \chi_{p, \nu}^2 \rangle$. First, we consider single-MBB models with 
$\beta$ spatially constant (see the black line in Figure \ref{fig:chi2_dirbe}).
$\beta$=1.57 yields the best fit, with $\chi^2_{\nu}$=2.51. This result is in 
excellent agreement with that of $\S$\ref{sec:global}, where we found the 
best-fit single-MBB model to have $\beta$=1.59.

We also evaluated $\chi^2_{\nu}$ for single-MBB models in which $\beta$ varies 
spatially. In these cases, we adopted the 0.5$^{\circ}$ resolution $\beta$ map 
from \cite{planckdust}. We started by calculating $\chi^2_{\nu}$ using the 
\cite{planckdust} temperature map, finding $\chi^2_{\nu}$=4.68. Note that in 
this case no per-pixel chi-squared minimization was involved, as we simply 
evaluated $\chi^2_{p}$ for each pixel based on the fully-specified 
\cite{planckdust} emission model. Next, we tested a single-MBB model for which 
we adopted the \cite{planckdust} $\beta$ map, but allowed the per-pixel 
temperature and normalization to vary so as to minimize $\chi^2_p$. In this 
case, we found $\chi^2_{\nu}$=2.51, effectively identical to the value found 
for the spatially constant $\beta$=1.57 single-MBB model. This is perhaps 
unsurprising, as the average $\beta$ value from \cite{planckdust} over the mask
in question is $\langle\beta\rangle$=1.58. This result does suggest, however, 
that in diffuse regions the half-degree variations in $\beta$ are not 
materially improving the goodness-of-fit over the full frequency range 100-3000
GHz relative to a model with appropriately chosen spatially constant $\beta$.

@@

@@

@@

@@

% in above paragraph, say which single-MBB beta(s) we find to be favored ?
